### 2018-05-30 paper/paper.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
                                                          % if you need a4paper
%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
                                                          % paper

\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
\overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\title{\LARGE \bf
Object Detection Based Behaviour with YOLO on Thymio
}

%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
%         \thanks{*Use the $\backslash$thanks command to put information here}\\
%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
%         University of Twente\\
%         7500 AE Enschede, The Netherlands\\
%         {\tt\small h.kwakernaak@autsubmit.com}}
%         \hspace*{ 0.5 in}
%         \parbox{3 in}{ \centering Pradeep Misra**
%         \thanks{**The footnote marks may be inserted manually}\\
%        Department of Electrical Engineering \\
%         Wright State University\\
%         Dayton, OH 45435, USA\\
%         {\tt\small pmisra@cs.wright.edu}}
%}

\author{Francesco Saverio Zuppichini$^{1}$ and Alessia Ruggeri$^{2}$% <-this % stops a space
\thanks{$^{1}$H. Kwakernaak is with Faculty of Electrical Engineering, Mathematics and Computer Science,
        University of Twente, 7500 AE Enschede, The Netherlands
        {\tt\small h.kwakernaak at papercept.net}}%
\thanks{$^{2}$P. Misra is with the Department of Electrical Engineering, Wright State University,
        Dayton, OH 45435, USA
        {\tt\small p.misra at ieee.org}}%
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The ability of classify in booth space and domain objects is encoded in an enormous variety of species on the planet. Recently, deep learning approaches has been develop to make machine able to mimic the same task with interesting results. In this paper we use a small two wheels robots, Thymio, with a frontal camera mounted to act based on the object detected in the surrounding. 
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}

This template, modified in MS Word 2003 and saved as ÒWord 97-2003 \& 6.0/95 Ð RTFÓ for the PC, provides authors with most of the formatting specifications needed for preparing electronic versions of their papers. All standard paper components have been specified for three reasons: (1) ease of use when formatting individual papers, (2) automatic compliance to electronic requirements that facilitate the concurrent or later production of electronic products, and (3) conformity of style throughout a conference proceedings. Margins, column widths, line spacing, and type styles are built-in; examples of the type styles are provided throughout this document and are identified in italic type, within parentheses, following the example. Some components, such as multi-leveled equations, graphics, and tables are not prescribed, although the various table text styles are provided. The formatter will need to create these components, incorporating the applicable criteria that follow.

\section{PROCEDURE FOR PAPER SUBMISSION}

\subsection{Selecting a Template (Heading 2)}

First, confirm that you have the correct template for your paper size. This template has been tailored for output on the US-letter paper size. Please do not use it for A4 paper since the margin requirements for A4 papers may be different from Letter paper size.

\subsection{Maintaining the Integrity of the Specifications}

The template is used to format your paper and style the text. All margins, column widths, line spaces, and text fonts are prescribed; please do not alter them. You may note peculiarities. For example, the head margin in this template measures proportionately more than is customary. This measurement and others are deliberate, using specifications that anticipate your paper as one part of the entire proceedings, and not as an independent document. Please do not revise any of the current designations

\section{MATH}

Before you begin to format your paper, first write and save the content as a separate text file. Keep your text and graphic files separate until after the text has been formatted and styled. Do not use hard tabs, and limit use of hard returns to only one return at the end of a paragraph. Do not add any kind of pagination anywhere in the paper. Do not number text heads-the template will do that for you.

Finally, complete content and organizational editing before formatting. Please take note of the following items when proofreading spelling and grammar:

\subsection{Abbreviations and Acronyms} Define abbreviations and acronyms the first time they are used in the text, even after they have been defined in the abstract. Abbreviations such as IEEE, SI, MKS, CGS, sc, dc, and rms do not have to be defined. Do not use abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}

\begin{itemize}

\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as Ò3.5-inch disk driveÓ.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ÒWb/m2Ó or Òwebers per square meterÓ, not Òwebers/m2Ó.  Spell out units when they appear in text: Ò. . . a few henriesÓ, not Ò. . . a few HÓ.
\item Use a zero before decimal points: Ò0.25Ó, not Ò.25Ó. Use Òcm3Ó, not ÒccÓ. (bullet list)

\end{itemize}

\subsection{Equations}

The equations are an exception to the prescribed specifications of this template. You will need to determine whether or not your equation should be typed using either the Times New Roman or the Symbol font (please no other font). To create multileveled equations, it may be necessary to treat the equation as a graphic and insert it into the text after your paper is styled. Number equations consecutively. Equation numbers, within parentheses, are to position flush right, as in (1), using a right tab stop. To make your equations more compact, you may use the solidus ( / ), the exp function, or appropriate exponents. Italicize Roman symbols for quantities and variables, but not Greek symbols. Use a long dash rather than a hyphen for a minus sign. Punctuate equations with commas or periods when they are part of a sentence, as in

$$
\alpha + \beta = \chi \eqno{(1)}
$$

Note that the equation is centered using a center tab stop. Be sure that the symbols in your equation have been defined before or immediately following the equation. Use Ò(1)Ó, not ÒEq. (1)Ó or Òequation (1)Ó, except at the beginning of a sentence: ÒEquation (1) is . . .Ó

\subsection{Some Common Mistakes}
\begin{itemize}

\item The word ÒdataÓ is plural, not singular.
\item The subscript for the permeability of vacuum ?0, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ÒoÓ.
\item In American English, commas, semi-/colons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ÒinsetÓ, not an ÒinsertÓ. The word alternatively is preferred to the word ÒalternatelyÓ (unless you really mean something that alternates).
\item Do not use the word ÒessentiallyÓ to mean ÒapproximatelyÓ or ÒeffectivelyÓ.
\item In your paper title, if the words Òthat usesÓ can accurately replace the word ÒusingÓ, capitalize the ÒuÓ; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ÒaffectÓ and ÒeffectÓ, ÒcomplementÓ and ÒcomplimentÓ, ÒdiscreetÓ and ÒdiscreteÓ, ÒprincipalÓ and ÒprincipleÓ.
\item Do not confuse ÒimplyÓ and ÒinferÓ.
\item The prefix ÒnonÓ is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ÒetÓ in the Latin abbreviation Òet al.Ó.
\item The abbreviation Òi.e.Ó means Òthat isÓ, and the abbreviation Òe.g.Ó means Òfor exampleÓ.

\end{itemize}

\section{USING THE TEMPLATE}

Use this sample document as your LaTeX source file to create your document. Save this file as {\bf root.tex}. You have to make sure to use the cls file that came with this distribution. If you use a different style file, you cannot expect to get required margins. Note also that when you are creating your out PDF file, the source file is only part of the equation. {\it Your \TeX\ $\rightarrow$ PDF filter determines the output file size. Even if you make all the specifications to output a letter file in the source - if you filter is set to produce A4, you will only get A4 output. }

It is impossible to account for all possible situation, one would encounter using \TeX. If you are using multiple \TeX\ files you must make sure that the ``MAIN`` source file is called root.tex - this is particularly important if your conference is using PaperPlaza's built in \TeX\ to PDF conversion tool.

\subsection{Headings, etc}

Text heads organize the topics on a relational, hierarchical basis. For example, the paper title is the primary text head because all subsequent material relates and elaborates on this one topic. If there are two or more sub-topics, the next level head (uppercase Roman numerals) should be used and, conversely, if there are not at least two sub-topics, then no subheads should be introduced. Styles named ÒHeading 1Ó, ÒHeading 2Ó, ÒHeading 3Ó, and ÒHeading 4Ó are prescribed.

\subsection{Figures and Tables}

Positioning Figures and Tables: Place figures and tables at the top and bottom of columns. Avoid placing them in the middle of columns. Large figures and tables may span across both columns. Figure captions should be below the figures; table heads should appear above the tables. Insert figures and tables after they are cited in the text. Use the abbreviation ÒFig. 1Ó, even at the beginning of a sentence.

\begin{table}[h]
\caption{An Example of a Table}
\label{table_example}
\begin{center}
\begin{tabular}{|c||c|}
\hline
One & Two\\
\hline
Three & Four\\
\hline
\end{tabular}
\end{center}
\end{table}

   \begin{figure}[thpb]
      \centering
      \framebox{\parbox{3in}{We suggest that you use a text box to insert a graphic (which is ideally a 300 dpi TIFF or EPS file, with all fonts embedded) because, in an document, this method is somewhat more stable than directly inserting a picture.
}}
      %\includegraphics[scale=1.0]{figurefile}
      \caption{Inductance of oscillation winding on amorphous
       magnetic core versus DC bias magnetic field}
      \label{figurelabel}
   \end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words rather than symbols or abbreviations when writing Figure axis labels to avoid confusing the reader. As an example, write the quantity ÒMagnetizationÓ, or ÒMagnetization, MÓ, not just ÒMÓ. If including units in the label, present them within parentheses. Do not label axes only with units. In the example, write ÒMagnetization (A/m)Ó or ÒMagnetization {A[m(1)]}Ó, not just ÒA/mÓ. Do not label axes with a ratio of quantities and units. For example, write ÒTemperature (K)Ó, not ÒTemperature/K.Ó

\section{CONCLUSIONS}

A conclusion section is not required. Although a conclusion may review the main points of the paper, do not replicate the abstract as the conclusion. A conclusion might elaborate on the importance of the work or suggest applications and extensions.

\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{APPENDIX}

Appendixes should appear before the acknowledgment.

\section*{ACKNOWLEDGMENT}

The preferred spelling of the word ÒacknowledgmentÓ in America is without an ÒeÓ after the ÒgÓ. Avoid the stilted expression, ÒOne of us (R. B. G.) thanks . . .Ó  Instead, try ÒR. B. G. thanksÓ. Put sponsor acknowledgments in the unnumbered footnote on the first page.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.

\begin{thebibliography}{99}

\bibitem{c1} G. O. Young, ÒSynthetic structure of industrial plastics (Book style with paper title and editor),Ó 	in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
\bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).	Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
\bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
\bibitem{c4} B. Smith, ÒAn approach to graphs of linear forms (Unpublished work style),Ó unpublished.
\bibitem{c5} E. H. Miller, ÒA note on reflector arrays (Periodical styleÑAccepted for publication),Ó IEEE Trans. Antennas Propagat., to be publised.
\bibitem{c6} J. Wang, ÒFundamentals of erbium-doped fiber amplifiers arrays (Periodical styleÑSubmitted for publication),Ó IEEE J. Quantum Electron., submitted for publication.
\bibitem{c7} C. J. Kaufman, Rocky Mountain Research Lab., Boulder, CO, private communication, May 1995.
\bibitem{c8} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ÒElectron spectroscopy studies on magneto-optical media and plastic substrate interfaces(Translation Journals style),Ó IEEE Transl. J. Magn.Jpn., vol. 2, Aug. 1987, pp. 740Ð741 [Dig. 9th Annu. Conf. Magnetics Japan, 1982, p. 301].
\bibitem{c9} M. Young, The Techincal Writers Handbook.  Mill Valley, CA: University Science, 1989.
\bibitem{c10} J. U. Duncombe, ÒInfrared navigationÑPart I: An assessment of feasibility (Periodical style),Ó IEEE Trans. Electron Devices, vol. ED-11, pp. 34Ð39, Jan. 1959.
\bibitem{c11} S. Chen, B. Mulgrew, and P. M. Grant, ÒA clustering technique for digital communications channel equalization using radial basis function networks,Ó IEEE Trans. Neural Networks, vol. 4, pp. 570Ð578, July 1993.
\bibitem{c12} R. W. Lucky, ÒAutomatic equalization for digital communication,Ó Bell Syst. Tech. J., vol. 44, no. 4, pp. 547Ð588, Apr. 1965.
\bibitem{c13} S. P. Bingulac, ÒOn the compatibility of adaptive controllers (Published Conference Proceedings style),Ó in Proc. 4th Annu. Allerton Conf. Circuits and Systems Theory, New York, 1994, pp. 8Ð16.
\bibitem{c14} G. R. Faulhaber, ÒDesign of service systems with priority reservation,Ó in Conf. Rec. 1995 IEEE Int. Conf. Communications, pp. 3Ð8.
\bibitem{c15} W. D. Doyle, ÒMagnetization reversal in films with biaxial anisotropy,Ó in 1987 Proc. INTERMAG Conf., pp. 2.2-1Ð2.2-6.
\bibitem{c16} G. W. Juette and L. E. Zeffanella, ÒRadio noise currents n short sections on bundle conductors (Presented Conference Paper style),Ó presented at the IEEE Summer power Meeting, Dallas, TX, June 22Ð27, 1990, Paper 90 SM 690-0 PWRS.
\bibitem{c17} J. G. Kreifeldt, ÒAn analysis of surface-detected EMG as an amplitude-modulated noise,Ó presented at the 1989 Int. Conf. Medicine and Biological Engineering, Chicago, IL.
\bibitem{c18} J. Williams, ÒNarrow-band analyzer (Thesis or Dissertation style),Ó Ph.D. dissertation, Dept. Elect. Eng., Harvard Univ., Cambridge, MA, 1993. 
\bibitem{c19} N. Kawasaki, ÒParametric study of thermal and chemical nonequilibrium nozzle flow,Ó M.S. thesis, Dept. Electron. Eng., Osaka Univ., Osaka, Japan, 1993.
\bibitem{c20} J. P. Wilkinson, ÒNonlinear resonant circuit devices (Patent style),Ó U.S. Patent 3 624 12, July 16, 1990.

\end{thebibliography}

\end{document}

### 2018-05-31 paper/paper.tex
Added section about YOLO

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{YOLO: REAL-TIME OBJECT DETECTION}
+
+YOLO is a trained model for real-time object detection.
+While prior work on object detection repurposes classifiers to perform detection, YOLO handle the object detection as a regression problem to spatially separated bounding boxes and associated class probabilities.
+YOLO avoids resorting to complex pipelines that are slow and hard to optimize; instead, it uses a single convolutional neural network that simultaneously predicts multiple bounding boxes and class probabilities for those boxes.
+Using YOLO, You Only Look Once at an image to predict what objects are present and where they are.
+
+YOLO neural network uses features from the entire image to predict each bounding box simultaneously across all classes.
+The convolutional neural network contains 24 convolutional layers, that extract features from the image, followed by 2 fully connected layers, whose aim is to predict the output probabilities and coordinates.
+The system divides the input image into an $S \times S$ grid; if the center of an object falls into a grid cell, that grid cell is responsible for detecting that object.
+Each grid cell predicts $B$ bounding boxes and confidence scores for those boxes.
+These confidence scores reflect how confident the model is that the box contains an object and also how accurate it thinks the box is that it predicts.
+There is also a fast version of YOLO, designed with a neural network with fewer convolutional leayers and fewer filters in those layers.
+
+YOLO is extremely fast, it reason globally about the image when making predictions, it learns generalizable representations of objects and it is open source.
+YOLO still lags behind other detection systems in accuracy; while it can quickly identify object in images, it struggles to precisely localize some objects, especially small ones.
+However, it is still the state-of-the-art model for object detection in real-time.
+
+For our project, we used the third version of YOLO, or YOLOv3, which has been improved by making it a little bigger than before, but more accurate.
+
 \section{INTRODUCTION}
@@
 \begin{thebibliography}{99}
+%%%%% Our bibliography
+\bibitem{c1} Y.
+Redmon, S.
+Divvala, R.
+Girshick, and A.
+Farhadi, ÒYou Only Look Once: Unified, Real-Time Object Detection,Ó University of Washington, Allen Institute for AI, Facebook AI Research, May 2016, http://pjreddie.com/yolo/.
+\bibitem{c2} Y. Redmon, and A. Farhadi, ÒYOLOv3: An Incremental Improvement,Ó University of Washington, Apr 2018.
 
-\bibitem{c1} G. O. Young, ÒSynthetic structure of industrial plastics (Book style with paper title and editor),Ó 	in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
-\bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).	Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
-\bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
-\bibitem{c4} B. Smith, ÒAn approach to graphs of linear forms (Unpublished work style),Ó unpublished.
-\bibitem{c5} E. H. Miller, ÒA note on reflector arrays (Periodical styleÑAccepted for publication),Ó IEEE Trans. Antennas Propagat., to be publised.
-\bibitem{c6} J. Wang, ÒFundamentals of erbium-doped fiber amplifiers arrays (Periodical styleÑSubmitted for publication),Ó IEEE J. Quantum Electron., submitted for publication.
-\bibitem{c7} C. J. Kaufman, Rocky Mountain Research Lab., Boulder, CO, private communication, May 1995.
-\bibitem{c8} Y.
+%%%%%  Bibliography templates
+%\bibitem{c1} G. O. Young, ÒSynthetic structure of industrial plastics (Book style with paper title and editor),Ó 	in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
+%\bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).	Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
+%\bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
+%\bibitem{c4} B. Smith, ÒAn approach to graphs of linear forms (Unpublished work style),Ó unpublished.
+%\bibitem{c5} E. H. Miller, ÒA note on reflector arrays (Periodical styleÑAccepted for publication),Ó IEEE Trans. Antennas Propagat., to be publised.
+%\bibitem{c6} J. Wang, ÒFundamentals of erbium-doped fiber amplifiers arrays (Periodical styleÑSubmitted for publication),Ó IEEE J. Quantum Electron., submitted for publication.
+%\bibitem{c7} C. J. Kaufman, Rocky Mountain Research Lab., Boulder, CO, private communication, May 1995.
+%\bibitem{c8} Y.
 Yorozu, M.
@@
 301].
-\bibitem{c9} M. Young, The Techincal Writers Handbook.  Mill Valley, CA: University Science, 1989.
-\bibitem{c10} J. U. Duncombe, ÒInfrared navigationÑPart I: An assessment of feasibility (Periodical style),Ó IEEE Trans. Electron Devices, vol. ED-11, pp. 34Ð39, Jan. 1959.
-\bibitem{c11} S.
+%\bibitem{c9} M. Young, The Techincal Writers Handbook.  Mill Valley, CA: University Science, 1989.
+%\bibitem{c10} J. U. Duncombe, ÒInfrared navigationÑPart I: An assessment of feasibility (Periodical style),Ó IEEE Trans. Electron Devices, vol. ED-11, pp. 34Ð39, Jan. 1959.
+%\bibitem{c11} S.
 Chen, B.
@@
 570Ð578, July 1993.
-\bibitem{c12} R. W. Lucky, ÒAutomatic equalization for digital communication,Ó Bell Syst. Tech. J., vol. 44, no. 4, pp. 547Ð588, Apr. 1965.
-\bibitem{c13} S.
+%\bibitem{c12} R. W. Lucky, ÒAutomatic equalization for digital communication,Ó Bell Syst. Tech. J., vol. 44, no. 4, pp. 547Ð588, Apr. 1965.
+%\bibitem{c13} S.
 P.
@@
 8Ð16.
-\bibitem{c14} G. R. Faulhaber, ÒDesign of service systems with priority reservation,Ó in Conf. Rec. 1995 IEEE Int. Conf. Communications, pp. 3Ð8.
-\bibitem{c15} W. D. Doyle, ÒMagnetization reversal in films with biaxial anisotropy,Ó in 1987 Proc. INTERMAG Conf., pp. 2.2-1Ð2.2-6.
-\bibitem{c16} G.
+%\bibitem{c14} G. R. Faulhaber, ÒDesign of service systems with priority reservation,Ó in Conf. Rec. 1995 IEEE Int. Conf. Communications, pp. 3Ð8.
+%\bibitem{c15} W. D. Doyle, ÒMagnetization reversal in films with biaxial anisotropy,Ó in 1987 Proc. INTERMAG Conf., pp. 2.2-1Ð2.2-6.
+%\bibitem{c16} G.
 W.
@@
 Zeffanella, ÒRadio noise currents n short sections on bundle conductors (Presented Conference Paper style),Ó presented at the IEEE Summer power Meeting, Dallas, TX, June 22Ð27, 1990, Paper 90 SM 690-0 PWRS.
-\bibitem{c17} J. G. Kreifeldt, ÒAn analysis of surface-detected EMG as an amplitude-modulated noise,Ó presented at the 1989 Int. Conf. Medicine and Biological Engineering, Chicago, IL.
-\bibitem{c18} J. Williams, ÒNarrow-band analyzer (Thesis or Dissertation style),Ó Ph.D. dissertation, Dept. Elect. Eng., Harvard Univ., Cambridge, MA, 1993. 
-\bibitem{c19} N. Kawasaki, ÒParametric study of thermal and chemical nonequilibrium nozzle flow,Ó M.S. thesis, Dept. Electron. Eng., Osaka Univ., Osaka, Japan, 1993.
-\bibitem{c20} J. P. Wilkinson, ÒNonlinear resonant circuit devices (Patent style),Ó U.S. Patent 3 624 12, July 16, 1990.
+%\bibitem{c17} J. G. Kreifeldt, ÒAn analysis of surface-detected EMG as an amplitude-modulated noise,Ó presented at the 1989 Int. Conf. Medicine and Biological Engineering, Chicago, IL.
+%\bibitem{c18} J. Williams, ÒNarrow-band analyzer (Thesis or Dissertation style),Ó Ph.D. dissertation, Dept. Elect. Eng., Harvard Univ., Cambridge, MA, 1993. 
+%\bibitem{c19} N. Kawasaki, ÒParametric study of thermal and chemical nonequilibrium nozzle flow,Ó M.S. thesis, Dept. Electron. Eng., Osaka Univ., Osaka, Japan, 1993.
+%\bibitem{c20} J. P. Wilkinson, ÒNonlinear resonant circuit devices (Patent style),Ó U.S. Patent 3 624 12, July 16, 1990.
 

### 2018-05-31 core/thymio-ros/SmartThymio.py
added obstance avoid code

@@ -24,15 +24,30 @@ class SmartThymio(Thymio, object):
         self.should_send = True # avoid automatic fire to the server
         self.draw = True
         self.HOST_URL = "http://192.168.168.64:8080"
-        res = requests.get('{}/model'.format(self.HOST_URL)).json()
-        self.colors, self.class_names = res['colors'], res['classes']
+        self.res = None
         self.global_step = 0
         self.camera_res  = (480,640)
         self.target = ['dog','teddy bear']
-        self.angular_pid = PID(Kd=5, Ki=0, Kp=1)
+        self.angular_pid = PID(Kd=5, Ki=0, Kp=0.5)
+        self.linear_pid = PID(Kd=5, Ki=0, Kp=0.5)
+        self.object_pid = PID(Kd=3, Ki=0, Kp=0.5)
+
         self.last_elapsed = 0
+        self.last_elapsed_sensors = 0
+
         self.MAX_TO_WAIT = 0.2
         self.p = threading.Thread()
+        self.obstacle = False
+        self.sensors_cache_values = np.zeros(7)
+
+        self.colors, self.class_names = self.get_model_info()
+
+
+    def get_model_info(self):
+
+        res = requests.get('{}/model'.format(self.HOST_URL)).json()
+
+        return res['colors'], res['classes']
 
     def draw_image(self, image, res, boxes=True, save=False):
 
@@ -74,7 +89,73 @@ class SmartThymio(Thymio, object):
         target_mid_p = np.abs(left - right) / 2
         offset = (left + target_mid_p)
         err = offset - img_mid_p
+
         return err, offset
+
+    def on_target(self, target_data):
+
+        box = self.get_box(target_data)
+
+        err, offset = self.get_error(box)
+
+        width, _ = self.camera_res
+        err = err / width  # normalize in %
+        dt = self.time_elapsed - self.last_elapsed
+        ang_vel = self.object_pid.step(err, dt)
+
+        # print('---------------')
+        # print('err   : {:.2f}'.format(err))
+        # print('offset: {:.2f}'.format(offset))
+        # print('dt    : {:.2f}'.format(dt))
+        # print('vel   : {:.2f}'.format(ang_vel))
+
+        self.last_elapsed = self.time_elapsed
+
+        # ang_vel /= 10
+
+        self.update_vel(Params(x=0.1), Params(z=-1 * ang_vel))
+
+    def on_receive_sensor_data(self, data, sensor_id, name):
[…]

### 2018-05-31 paper/paper.tex
added introduction

@@
 Recently, deep learning approaches has been develop to make machine able to mimic the same task with interesting results.
-In this paper we use a small two wheels robots, Thymio, with a frontal camera mounted to act based on the object detected in the surrounding.
+With this paper, we propose minimal architecture to archive the same goal using atwo wheels robots, Thymio, with a frontal camera mounted to act based on the object detected in the surrounding.
 \end{abstract}
+\section{Introduction}
+Find object in space by identify their identity and their coordinate is a basic task that almost each animal is able to accomplish by feeding the input of their eyes to the brain.
+The ability to solve this problem is extremely important in robotics where a machine needs to act accordingly based on its surrounding.
+With  our architecture, only the raw data from the camera are used as input to an Object Detection and the decision are based directly on the prediction without the need of any other sensor.
 
+The paper is structured as follow, we first describer the architecture by showing each individual part of the topology  and how they interact.
+Then, we discuss the challenges during the development process and finally we show the results.
+
+\section{Architecture}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{INTRODUCTION}
-
-This template, modified in MS Word 2003 and saved as ÒWord 97-2003 \& 6.0/95 Ð RTFÓ for the PC, provides authors with most of the formatting specifications needed for preparing electronic versions of their papers.
-All standard paper components have been specified for three reasons: (1) ease of use when formatting individual papers, (2) automatic compliance to electronic requirements that facilitate the concurrent or later production of electronic products, and (3) conformity of style throughout a conference proceedings.
-Margins, column widths, line spacing, and type styles are built-in; examples of the type styles are provided throughout this document and are identified in italic type, within parentheses, following the example.
-Some components, such as multi-leveled equations, graphics, and tables are not prescribed, although the various table text styles are provided.
-The formatter will need to create these components, incorporating the applicable criteria that follow.
-
-\section{PROCEDURE FOR PAPER SUBMISSION}
-
-\subsection{Selecting a Template (Heading 2)}
-
-First, confirm that you have the correct template for your paper size.
-This template has been tailored for output on the US-letter paper size.
-Please do not use it for A4 paper since the margin requirements for A4 papers may be different from Letter paper size.
-
-\subsection{Maintaining the Integrity of the Specifications}
-
-The template is used to format your paper and style the text.
-All margins, column widths, line spaces, and text fonts are prescribed; please do not alter them.
-You may note peculiarities.
-For example, the head margin in this template measures proportionately more than is customary.
-This measurement and others are deliberate, using specifications that anticipate your paper as one part of the entire proceedings, and not as an independent document.
-Please do not revise any of the current designations
-
-\section{MATH}
-
-Before you begin to format your paper, first write and save the content as a separate text file.
-Keep your text and graphic files separate until after the text has been formatted and styled.
-Do not use hard tabs, and limit use of hard returns to only one return at the end of a paragraph.
-Do not add any kind of pagination anywhere in the paper.
-Do not number text heads-the template will do that for you.
-
-Finally, complete content and organizational editing before formatting. Please take note of the following items when proofreading spelling and grammar:
-
-\subsection{Abbreviations and Acronyms} Define abbreviations and acronyms the first time they are used in the text, even after they have been defined in the abstract.
-Abbreviations such as IEEE, SI, MKS, CGS, sc, dc, and rms do not have to be defined.
-Do not use abbreviations in the title or heads unless they are unavoidable.
-
-\subsection{Units}
-
-\begin{itemize}
-
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as Ò3.5-inch disk driveÓ.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ÒWb/m2Ó or Òwebers per square meterÓ, not Òwebers/m2Ó.
-Spell out units when they appear in text: Ò.
-.
-.
-a few henriesÓ, not Ò.
-.
-.
-a few HÓ.
-\item Use a zero before decimal points: Ò0.25Ó, not Ò.25Ó. Use Òcm3Ó, not ÒccÓ. (bullet list)
-
-\end{itemize}
-
-\subsection{Equations}
-
-The equations are an exception to the prescribed specifications of this template.
-You will need to determine whether or not your equation should be typed using either the Times New Roman or the Symbol font (please no other font).
-To create multileveled equations, it may be necessary to treat the equation as a graphic and insert it into the text after your paper is styled.
-Number equations consecutively.
-Equation numbers, within parentheses, are to position flush right, as in (1), using a right tab stop.
-To make your equations more compact, you may use the solidus ( / ), the exp function, or appropriate exponents.
-Italicize Roman symbols for quantities and variables, but not Greek symbols.
-Use a long dash rather than a hyphen for a minus sign.
-Punctuate equations with commas or periods when they are part of a sentence, as in
-
-$$
-\alpha + \beta = \chi \eqno{(1)}
-$$
-
-Note that the equation is centered using a center tab stop.
-Be sure that the symbols in your equation have been defined before or immediately following the equation.
-Use Ò(1)Ó, not ÒEq.
-(1)Ó or Òequation (1)Ó, except at the beginning of a sentence: ÒEquation (1) is .
-.
-.Ó
-
-\subsection{Some Common Mistakes}
-\begin{itemize}
-
-\item The word ÒdataÓ is plural, not singular.
-\item The subscript for the permeability of vacuum ?0, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ÒoÓ.
-\item In American English, commas, semi-/colons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ÒinsetÓ, not an ÒinsertÓ. The word alternatively is preferred to the word ÒalternatelyÓ (unless you really mean something that alternates).
-\item Do not use the word ÒessentiallyÓ to mean ÒapproximatelyÓ or ÒeffectivelyÓ.
-\item In your paper title, if the words Òthat usesÓ can accurately replace the word ÒusingÓ, capitalize the ÒuÓ; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ÒaffectÓ and ÒeffectÓ, ÒcomplementÓ and ÒcomplimentÓ, ÒdiscreetÓ and ÒdiscreteÓ, ÒprincipalÓ and ÒprincipleÓ.
-\item Do not confuse ÒimplyÓ and ÒinferÓ.
-\item The prefix ÒnonÓ is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ÒetÓ in the Latin abbreviation Òet al.Ó.
-\item The abbreviation Òi.e.Ó means Òthat isÓ, and the abbreviation Òe.g.Ó means Òfor exampleÓ.
-
-\end{itemize}
-
-\section{USING THE TEMPLATE}
-
-Use this sample document as your LaTeX source file to create your document.
-Save this file as {\bf root.tex}.
-You have to make sure to use the cls file that came with this distribution.
-If you use a different style file, you cannot expect to get required margins.
-Note also that when you are creating your out PDF file, the source file is only part of the equation.
-{\it Your \TeX\ $\rightarrow$ PDF filter determines the output file size.
-Even if you make all the specifications to output a letter file in the source - if you filter is set to produce A4, you will only get A4 output.
-}
-
-It is impossible to account for all possible situation, one would encounter using \TeX.
-If you are using multiple \TeX\ files you must make sure that the ``MAIN`` source file is called root.tex - this is particularly important if your conference is using PaperPlaza's built in \TeX\ to PDF conversion tool.
-
-\subsection{Headings, etc}
-
-Text heads organize the topics on a relational, hierarchical basis.
-For example, the paper title is the primary text head because all subsequent material relates and elaborates on this one topic.
-If there are two or more sub-topics, the next level head (uppercase Roman numerals) should be used and, conversely, if there are not at least two sub-topics, then no subheads should be introduced.
-Styles named ÒHeading 1Ó, ÒHeading 2Ó, ÒHeading 3Ó, and ÒHeading 4Ó are prescribed.
-
-\subsection{Figures and Tables}
-
-Positioning Figures and Tables: Place figures and tables at the top and bottom of columns.
-Avoid placing them in the middle of columns.
-Large figures and tables may span across both columns.
-Figure captions should be below the figures; table heads should appear above the tables.
-Insert figures and tables after they are cited in the text.
-Use the abbreviation ÒFig.
-1Ó, even at the beginning of a sentence.
-
-\begin{table}[h]
-\caption{An Example of a Table}
-\label{table_example}
-\begin{center}
-\begin{tabular}{|c||c|}
-\hline
-One & Two\\
-\hline
-Three & Four\\
-\hline
-\end{tabular}
-\end{center}
-\end{table}
-
-   \begin{figure}[thpb]
-      \centering
-      \framebox{\parbox{3in}{We suggest that you use a text box to insert a graphic (which is ideally a 300 dpi TIFF or EPS file, with all fonts embedded) because, in an document, this method is somewhat more stable than directly inserting a picture.
-}}
-      %\includegraphics[scale=1.0]{figurefile}
-      \caption{Inductance of oscillation winding on amorphous
-       magnetic core versus DC bias magnetic field}
-      \label{figurelabel}
-   \end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels.
-Use words rather than symbols or abbreviations when writing Figure axis labels to avoid confusing the reader.
-As an example, write the quantity ÒMagnetizationÓ, or ÒMagnetization, MÓ, not just ÒMÓ.
-If including units in the label, present them within parentheses.
-Do not label axes only with units.
-In the example, write ÒMagnetization (A/m)Ó or ÒMagnetization {A[m(1)]}Ó, not just ÒA/mÓ.
-Do not label axes with a ratio of quantities and units.
-For example, write ÒTemperature (K)Ó, not ÒTemperature/K.Ó
-
-\section{CONCLUSIONS}
-
-A conclusion section is not required.
-Although a conclusion may review the main points of the paper, do not replicate the abstract as the conclusion.
-A conclusion might elaborate on the importance of the work or suggest applications and extensions.
-
-\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
-                                  % on the last page of the document manually. It shortens
-                                  % the textheight of the last page by a suitable amount.
-                                  % This command does not take effect until the next page
-                                  % so it should come on the page before the last. Make
-                                  % sure that you do not shorten the textheight too much.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{APPENDIX}
-
-Appendixes should appear before the acknowledgment.
-
-\section*{ACKNOWLEDGMENT}
-
-The preferred spelling of the word ÒacknowledgmentÓ in America is without an ÒeÓ after the ÒgÓ.
-Avoid the stilted expression, ÒOne of us (R.
-B.
-G.) thanks .
-.
-.Ó  Instead, try ÒR.
-B.
-G.
-thanksÓ.
-Put sponsor acknowledgments in the unnumbered footnote on the first page.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.
+\section{Results}
+\section{Conclusion}
 

### 2018-05-31 paper/paper.tex
changes in the paper

@@
 % on the last page of the document
+
+\usepackage{biblatex}
+\bibliography{paper}
 
@@
 
-\author{Francesco Saverio Zuppichini$^{1}$ and Alessia Ruggeri$^{2}$% <-this % stops a space
-\thanks{$^{1}$H. Kwakernaak is with Faculty of Electrical Engineering, Mathematics and Computer Science,
-        University of Twente, 7500 AE Enschede, The Netherlands
-        {\tt\small h.kwakernaak at papercept.net}}%
-\thanks{$^{2}$P. Misra is with the Department of Electrical Engineering, Wright State University,
-        Dayton, OH 45435, USA
-        {\tt\small p.misra at ieee.org}}%
-}
+\author{Francesco Saverio Zuppichini$^{1}$ and Alessia Ruggeri$^{2}$}% <-this % stops a space
 
@@
 \section{Architecture}
+Our architecture is composed by:
+\begin{enumerate}
+	\item A robot with a mounted camera and onboard computer with a running ROS node
+	\item A web server running the Object Detection model
+	\item A ROS node running on a local machine
+\end{enumerate}
+As robot, we used the \emph{MightyThymio} \cite{guzzi2018eaai}.
+A robot develop on top of the Thymio, a small mass-produced mobile usually used in primary  and secondary education.
+The MightyThymio has a powerful Odroid C1 on board, a 1GB quad-core ARM Linux machine, with a HD camera mounted on top.
+The authors also implemented a ROS node to communicate with it and open-sourced the code.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-YOLO is a trained model for real-time object detection.
+YOLO \cite{DBLP:conf/cvpr/RedmonDGF16} is a trained model for real-time object detection.
 While prior work on object detection repurposes classifiers to perform detection, YOLO handle the object detection as a regression problem to spatially separated bounding boxes and associated class probabilities.
@@
 
-For our project, we used the third version of YOLO, or YOLOv3, which has been improved by making it a little bigger than before, but more accurate.
+For our project, we used the third version of YOLO, or YOLOv3 \cite{Yolo3}, which has been improved by making it a little bigger than before, but more accurate.
 
@@
 
-\begin{thebibliography}{99}
-%%%%% Our bibliography
-\bibitem{c1} Y.
+\printbibliography
+
+%\begin{thebibliography}{99}
+%%%%%% Our bibliography
+%\bibitem{c1} Y.
 Redmon, S.
@@
 Farhadi, ÒYou Only Look Once: Unified, Real-Time Object Detection,Ó University of Washington, Allen Institute for AI, Facebook AI Research, May 2016, http://pjreddie.com/yolo/.
-\bibitem{c2} Y. Redmon, and A. Farhadi, ÒYOLOv3: An Incremental Improvement,Ó University of Washington, Apr 2018.
+%\bibitem{c2} Y. Redmon, and A. Farhadi, ÒYOLOv3: An Incremental Improvement,Ó University of Washington, Apr 2018.
+%
+%\bibitem{c3} Guzzi, Jérôme and Giusti, Alessandro and Di Caro, Gianni A. and Gambardella, Luca M.,Mighty Thymio for Higher-Level Robotics Education, IDSIA, 2018.
 

### 2018-05-31 core/thymio-ros/main.py
basic behavior

@@ -1,12 +1,17 @@
 from Thymio import Thymio
 from SmartThymio import SmartThymio
 from utils import Params
+from thymio_msgs.msg import Led
 import rospy
+import numpy as np
+
+# thymio = Thymio('thymio29')
 
 thymio = SmartThymio('thymio29')
 
-
 # thymio.stop()
 rospy.sleep(1.)
+# mask = np.array([1.0,1.0,1.0,0,0,0,1,1])
+# thymio.led_subscriber.publish(Led(values=np.zeros(8), id=0))
+# thymio.led_subscriber.publish(Led(values=mask, id=0))
 thymio.move(Params(0),Params())
-# rospy.sleep(1.)

### 2018-05-31 core/thymio-ros/utils.py

@@ -67,3 +67,13 @@ def unbox(res):
     out_classes_idx = list(map(lambda x: x['class_idx'], res))
 
     return out_scores, out_boxes, out_classes, out_classes_idx
+
+
+def rect_area(rect):
+    top, left, bottom, right = rect
+    b = right - left
+    h = bottom - top
+
+
+    return b*h
+

### 2018-05-31 paper/paper.tex

@@
 \title{\LARGE \bf
-Object Detection Based Behaviour with YOLO on Thymio
+Object Detection-Based Behaviour using YOLO on Thymio
 }
@@
 \begin{abstract}
-The ability of classify in booth space and domain objects is encoded in an enormous variety of species on the planet.
-Recently, deep learning approaches has been develop to make machine able to mimic the same task with interesting results.
-With this paper, we propose minimal architecture to archive the same goal using atwo wheels robots, Thymio, with a frontal camera mounted to act based on the object detected in the surrounding.
+The ability to classify in booth space and domain objects is encoded in an enormous variety of species on the planet.
+Recently, deep learning approaches have been developed to make machines able to mimic the same task with interesting results.
+With this paper, we propose a minimal architecture to archive the same goal using a two wheels robots, the Thymio, with a mounted frontal camera in order to act based on the object detected in the surrounding.
 \end{abstract}
 \section{Introduction}
-Find object in space by identify their identity and their coordinate is a basic task that almost each animal is able to accomplish by feeding the input of their eyes to the brain.
-The ability to solve this problem is extremely important in robotics where a machine needs to act accordingly based on its surrounding.
-With  our architecture, only the raw data from the camera are used as input to an Object Detection and the decision are based directly on the prediction without the need of any other sensor.
+Finding objects in space by identifying their identity and their coordinates is a basic task that almost each animal is able to accomplish by feeding the inputs from their eyes to the brain.
+The ability to solve this problem is extremely important in robotics, where a machine needs to act accordingly based on its surrounding.
+With our architecture, only the raw data from the camera are used as input to an Object Detection model and the decision are based directly on the prediction, without the need of any other sensor.
 
-The paper is structured as follow, we first describer the architecture by showing each individual part of the topology  and how they interact.
-Then, we discuss the challenges during the development process and finally we show the results.
+The paper is structured as follows: we will first describe the architecture by showing each individual part of the topology and how they interact; then, we will discuss the challenges during the development process and finally we will show the results.
 
@@
 \begin{enumerate}
-	\item A robot with a mounted camera and onboard computer with a running ROS node
+	\item A robot with a mounted camera and an on-board computer with a running ROS node
 	\item A web server running the Object Detection model
@@
 \end{enumerate}
-As robot, we used the \emph{MightyThymio} \cite{guzzi2018eaai}.
-A robot develop on top of the Thymio, a small mass-produced mobile usually used in primary  and secondary education.
+As a robot, we used the \emph{MightyThymio} \cite{guzzi2018eaai}, which is a robot developed on top of the Thymio, a small mass-produced mobile robot usually used in primary and secondary education.
 The MightyThymio has a powerful Odroid C1 on board, a 1GB quad-core ARM Linux machine, with a HD camera mounted on top.
@@
 
-\end{thebibliography}
-
 \end{document}

### 2018-05-31 paper/paper.tex
Added things to paper

@@
 \end{abstract}
+
 \section{Introduction}
+
 Finding objects in space by identifying their identity and their coordinates is a basic task that almost each animal is able to accomplish by feeding the inputs from their eyes to the brain.
@@
 
-\section{Architecture}
+\section{Architecture overview}
+
 Our architecture is composed by:
 \begin{enumerate}
-	\item A robot with a mounted camera and an on-board computer with a running ROS node
-	\item A web server running the Object Detection model
-	\item A ROS node running on a local machine
+	\item A robot with a mounted camera and an on-board computer with a running ROS node;
+	\item A web server running the Object Detection model;
+	\item A ROS node running on a local machine.
 \end{enumerate}
@@
 The authors also implemented a ROS node to communicate with it and open-sourced the code.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{YOLO: REAL-TIME OBJECT DETECTION}
+
+\subsection{Configuration}
+
+In our project, the MightyThymio has the same configuration proposed in \cite{guzzi2018eaai}.
+On the on-board computer of the robot there is a running ROS node that can publish and subscribe in order to communicate with its sensors: it can have information from the proximity sensors to avoid hitting obstacles, it can take images from the mounted camera, it can use the leds to indicate an object or a direction, and more.
+On the local machine there is another running ROS node that specifies the behaviour of the MightyThymio based on the presence of specific objects around him.
+
+%Subscribe thyme event of camera, from whom compressed images, encoded in strings, then we send to the server, the server decode the compressed images and send prediction.
+After prediction, if class is target, for example person, the server send the person and bounding box.
+If the timeo see the person, it moves verso the person keeping her in the centre.
+So if the person moves, the timeo moves to keep the bounding box in the centre of the camera.
+So using only the image we can tell timeo to follow a target, without knowing the position of target or of thimeo.
+%The rod node is a module that can be put where you want.
+
+\subsection{ROS: Robot Operating System}
+ROS is a robotics middleware that provides libraries and tools to help software developers create robot applications by supplying hardware abstraction, device drivers, message-passing, and more.
+One main concepts in ROS is the node, which is included in the level of Computation Graph, the peer-to-peer network of ROS processes that are processing data together.
+Nodes are processes that perform computation; a robot control system usually comprises many nodes, that act as modules.
+
+\subsection{YOLO: Real-Time Object Detection}
 
@@
 For our project, we used the third version of YOLO, or YOLOv3 \cite{Yolo3}, which has been improved by making it a little bigger than before, but more accurate.
+
+\section{Code}
+
+\section{Server}
 

### 2018-06-01 core/thymio-ros/SmartThymio.py
added code from ubuntu

@@ -14,7 +14,7 @@ from time import time
 from time import sleep
 import threading
 from thymio_msgs.msg import Led
-
+import sys
 IMAGE_SAVE_DIR = './image_save/'
 
 class SmartThymio(Thymio, object):
@@ -30,7 +30,7 @@ class SmartThymio(Thymio, object):
         self.res = None
         self.global_step = 0
         self.camera_res  = (480,640)
-        self.target = ['dog','teddy bear', 'chair']
+        self.target = []
         self.angular_pid = PID(Kd=5, Ki=0, Kp=0.5)
         self.linear_pid = PID(Kd=5, Ki=0, Kp=0.5)
         self.object_pid = PID(Kd=3, Ki=0, Kp=0.5)
@@ -59,9 +59,11 @@ class SmartThymio(Thymio, object):
                                         is_array=True)
 
             image = cv2.cvtColor(np.array(pil_image), cv2.COLOR_RGB2BGR)
+
         if save:
             file_name = '{}'.format(self.global_step)
-            np.save(IMAGE_SAVE_DIR + file_name, image)
+            cv2.imwrite(IMAGE_SAVE_DIR + file_name + '.jpg',image)
+            np.save(IMAGE_SAVE_DIR  + file_name, image)
             with open('{}{}.json'.format(IMAGE_SAVE_DIR,file_name), 'w') as f:
                 json.dump(res.json(), f)
 
@@ -115,13 +117,12 @@ class SmartThymio(Thymio, object):
         self.led_subscriber.publish(Led(values=mask, id=id))
 
     def on_target(self, target_data):
-        print('Found {}').format(target_data['class'])
         box = self.get_box(target_data)
 
         err, offset = self.get_error(box)
 
         height, width = self.camera_res
-        err = err / height  # normalize in %
+        err = err / width  # normalize in %
         dt = self.time_elapsed - self.last_elapsed
         ang_vel = self.object_pid.step(err, dt)
 
@@ -130,13 +131,28 @@ class SmartThymio(Thymio, object):
         # print('offset: {:.2f}'.format(offset))
         # print('dt    : {:.2f}'.format(dt))
         # print('vel   : {:.2f}'.format(ang_vel))
+        # print('Found {}').format(target_data['class'])
 
         self.last_elapsed = self.time_elapsed
-
+        # print("{},".format(err))
         # ang_vel /= 10
         self.on_target_turn_on_leds(box)
 
         self.update_vel(Params(self.FORWARD_VEL), Params(z=-ang_vel))
+
[…]

### 2018-06-01 core/thymio-ros/main.py

@@ -9,9 +9,7 @@ import numpy as np
 
 thymio = SmartThymio('thymio29')
 
-# thymio.stop()
 rospy.sleep(1.)
-# mask = np.array([1.0,1.0,1.0,0,0,0,1,1])
-# thymio.led_subscriber.publish(Led(values=np.zeros(8), id=0))
-# thymio.led_subscriber.publish(Led(values=mask, id=0))
+
+thymio.interactive()
 thymio.move(Params(0),Params())

### 2018-06-01 paper/paper.tex
updated paper, addedd final code for the  thymio

@@
 \begin{abstract}
-The ability to classify in booth space and domain objects is encoded in an enormous variety of species on the planet.
+The ability to classify objects in both space and domain is encoded in an enormous variety of species on the planet.
 Recently, deep learning approaches have been developed to make machines able to mimic the same task with interesting results.
-With this paper, we propose a minimal architecture to archive the same goal using a two wheels robots, the Thymio, with a mounted frontal camera in order to act based on the object detected in the surrounding.
+With this paper, we propose a minimal architecture to archive the same goal using a two wheels robots, the Thymio, with a mounted frontal camera in order to make it act based on the objects detected in the surrounding.
 \end{abstract}
@@
 \section{Architecture overview}
-
-Our architecture is composed by:
+We used ROS\cite{ROS} as operating system to develop and deploy our code on the Thymio. Our architecture is composed by:
 \begin{enumerate}
-	\item A robot with a mounted camera and an on-board computer with a running ROS node;
-	\item A web server running the Object Detection model;
-	\item A ROS node running on a local machine.
+	\item A robot with a mounted camera and an on-board computer
+	\item A web server running the Object Detection model
+	\item A ROS node running on a local machine that moves the robot
 \end{enumerate}
@@
 
-\subsection{Configuration}
+\subsection*{MightyThymio}
 
 In our project, the MightyThymio has the same configuration proposed in \cite{guzzi2018eaai}.
-On the on-board computer of the robot there is a running ROS node that can publish and subscribe in order to communicate with its sensors: it can have information from the proximity sensors to avoid hitting obstacles, it can take images from the mounted camera, it can use the leds to indicate an object or a direction, and more.
-On the local machine there is another running ROS node that specifies the behaviour of the MightyThymio based on the presence of specific objects around him.
+Briefly, the on-board computer expose the Thymios sensors through ROS.
+Thus, another ROS node can publish and subscribe in order to communicate with its sensors.
+For example, we can subscribe to the \emph{camera sensors} to get information from the proximity sensors to avoid hitting obstacles.
+Also, we can simply subscribe to the camera's topic to get both compressed and uncompressed images.
 
@@
 
-\subsection{ROS: Robot Operating System}
-ROS is a robotics middleware that provides libraries and tools to help software developers create robot applications by supplying hardware abstraction, device drivers, message-passing, and more.
-One main concepts in ROS is the node, which is included in the level of Computation Graph, the peer-to-peer network of ROS processes that are processing data together.
-Nodes are processes that perform computation; a robot control system usually comprises many nodes, that act as modules.
+\subsection*{Local ROS node}
+We created a new ROS node to communicate with the running node on the MightyThymio in order to make it act accordingly with a specified behaviour based on the object detected by the model.
+The user specifies a set of target classes, for example \emph{dog} and \emph{cat}.
+Then our node, after having subscribed to the camera topic of the MightyThymio, sends the fetched image to the model trough an HTTP request and gets the bounding boxes for the detected classes.
+If there is no target prediction, the robot enters in \texttt{exploration} mode and starts spinning around.
+When one or more of the target classes are found, then our robot will start going forward while keeping the bounding box of the target in the centre of the camera in order to follow it.
+If we detect more classes, then the closest, which is represented by the biggest bounding box area, will be followed.
+In addiction, we have an obstacle-avoiding algorithm in order to properly stop the Thymio before it hits the target.
+
+\subsection*{Object Detection REST-API Web Server}
+We used pre-trained YOLO\cite{DBLP:conf/cvpr/RedmonDGF16}, the state-of-the-art real-time object detection model, to predict the bounding boxes for each class.
+The model was trained on the COCO(Common Object in Context)\cite{COCO} Dataset, that contains 80 classes.
+
+On top of that, we built a REST-API Web Server using Python3 and Flask, a micro-framework to create Web Servers, to make the model accessible from the Web.
+
+We decided to decouple the logic behind the robot behaviour and the model in order to make our architecture more scalable.
+For instance, if needed, we can deploy our model in the cloud while keeping the running ROS code intact.
+
+\section{}
 
@@
 The convolutional neural network contains 24 convolutional layers, that extract features from the image, followed by 2 fully connected layers, whose aim is to predict the output probabilities and coordinates.
-The system divides the input image into an $S \times S$ grid; if the center of an object falls into a grid cell, that grid cell is responsible for detecting that object.
+The system divides the input image into an $S \times S$ grid; if the centre of an object falls into a grid cell, that grid cell is responsible for detecting that object.
 Each grid cell predicts $B$ bounding boxes and confidence scores for those boxes.
 These confidence scores reflect how confident the model is that the box contains an object and also how accurate it thinks the box is that it predicts.
-There is also a fast version of YOLO, designed with a neural network with fewer convolutional leayers and fewer filters in those layers.
+There is also a fast version of YOLO, designed with a neural network with fewer convolutional layers and fewer filters in those layers.
 
@@
 \section{Results}
+
 \section{Conclusion}
+In this paper we presented a light and scalable architecture that uses a real-time Object Detection model to correctly find objects in the surrounding environment and to perform actions based on that.
+Since we only require a camera, our work can be used into similar robots running ROS with the correct hardware in order to extend their functionalities.
+Furthermore, since we used YOLO to perform the classification task, the model can be easily re-trained with other classes to expand the context domain.
+This symbiosis between Machine Learning and Robotic highlights the power of both areas by creating new interesting user cases and scenarios in which both disciplines can shine.
 

### 2018-06-01 core/thymio-ros/SmartThymio.py

@@ -30,7 +30,7 @@ class SmartThymio(Thymio, object):
         self.res = None
         self.global_step = 0
         self.camera_res  = (480,640)
-        self.target = []
+        self.target = ['cup']
         self.angular_pid = PID(Kd=5, Ki=0, Kp=0.5)
         self.linear_pid = PID(Kd=5, Ki=0, Kp=0.5)
         self.object_pid = PID(Kd=3, Ki=0, Kp=0.5)
@@ -43,6 +43,7 @@ class SmartThymio(Thymio, object):
 
         self.p = threading.Thread()
         self.obstacle = False
+        self.DEBUG = False
         self.N_LEDS = 5
         self.colors, self.class_names = self.get_model_info()
 
@@ -59,13 +60,10 @@ class SmartThymio(Thymio, object):
                                         is_array=True)
 
             image = cv2.cvtColor(np.array(pil_image), cv2.COLOR_RGB2BGR)
-
+            self.image_with_boxes = image
         if save:
             file_name = '{}'.format(self.global_step)
             cv2.imwrite(IMAGE_SAVE_DIR + file_name + '.jpg',image)
-            np.save(IMAGE_SAVE_DIR  + file_name, image)
-            with open('{}{}.json'.format(IMAGE_SAVE_DIR,file_name), 'w') as f:
-                json.dump(res.json(), f)
 
         cv2.imshow('image', image)
         cv2.waitKey(1)
@@ -87,7 +85,6 @@ class SmartThymio(Thymio, object):
         return box
 
     def get_error(self, box):
-
         height, width = self.camera_res
         img_mid_p = width // 2
         top, left, bottom, right = box
@@ -126,16 +123,16 @@ class SmartThymio(Thymio, object):
         dt = self.time_elapsed - self.last_elapsed
         ang_vel = self.object_pid.step(err, dt)
 
-        # print('---------------')
-        # print('err   : {:.2f}'.format(err))
-        # print('offset: {:.2f}'.format(offset))
-        # print('dt    : {:.2f}'.format(dt))
-        # print('vel   : {:.2f}'.format(ang_vel))
-        # print('Found {}').format(target_data['class'])
+        if self.DEBUG:
+            print('---------------')
+            print('err   : {:.2f}'.format(err))
+            print('offset: {:.2f}'.format(offset))
+            print('dt    : {:.2f}'.format(dt))
+            print('vel   : {:.2f}'.format(ang_vel))
[…]

### 2018-06-01 paper/paper.tex
paper updates

@@
 
+\usepackage{listings}
 \usepackage{biblatex}
 \bibliography{paper}
-
+\usepackage{float}
+\usepackage{amsmath}
+\usepackage{graphicx}
 % The following packages can be found on http:\\www.ctan.org
@@
 %\usepackage{amssymb}  % assumes amsmath package installed
+\lstset{
+%  basicstyle=\ttfamily,
+  columns=fullflexible,
+  frame=single,
+  breaklines=true,
+  basicstyle=\small
+}
 
@@
 
-Finding objects in space by identifying their identity and their coordinates is a basic task that almost each animal is able to accomplish by feeding the inputs from their eyes to the brain.
+Finding objects in space by identifying their identity and their coordinates is a basic task that almost each animal is able to accomplish.
 The ability to solve this problem is extremely important in robotics, where a machine needs to act accordingly based on its surrounding.
 With our architecture, only the raw data from the camera are used as input to an Object Detection model and the decision are based directly on the prediction, without the need of any other sensor.
+
+Specifically, our robot will wait for an user-specified class, e.g.
+\emph{dog}, and, when found, it moves towards the object by keeping it in the middle of its view.
+We also implemented a PID based algorithm to avoid obstacles and properly stop in front of founded item.
 
@@
 
+\begin{figure}[H]
+\centering
+\includegraphics[width=\linewidth]{assembled_myt}	
+\caption{The MightyThymio}
+\end{figure}
 %Subscribe thyme event of camera, from whom compressed images, encoded in strings, then we send to the server, the server decode the compressed images and send prediction.
@@
 On top of that, we built a REST-API Web Server using Python3 and Flask, a micro-framework to create Web Servers, to make the model accessible from the Web.
-
 We decided to decouple the logic behind the robot behaviour and the model in order to make our architecture more scalable.
@@
 
+We following endpoints are available:
+\begin{lstlisting}
+GET /model
+POST /prediction  --image --size --compress
+\end{lstlisting}
+Each of them returns a JSON serialised response.
+The \texttt{/model} endpoint is used to get informations about the model on the server.
+These informations are the classes and the colour associated to each one of them.
+It follows a snapshot of the response:
+\begin{lstlisting}
+{
+    "classes": [ "person", "bicycle", "car", "motorbike", "aeroplane", ... ]
+    "colors": [[255, 38, 0], [0, 63, 255], ... ]   
+ }
+\end{lstlisting}
+The client can get a prediction by sending and image to \texttt{/prediction}.
+Also, it can specify whatever the  image is compressed or no and if the server should resize it before feed it to the model.
+In our case, we send a compressed image directly taken from the MightyThymio after subscribed to the \texttt{/camera/compressed} topic and we define the resize size to (190,190).
+The small size is due low computational power since we had no access to a GPU.
+The response looks like:
+\begin{lstlisting}
+{'res': [{'boxes': [96.21580505371094,
+                    219.6134033203125,
+                    437.66387939453125,
+                    594.16748046875],
+          'class': 'bicycle',
+          'class_idx': 1,
+          'score': 0.48406994342803955}, ...
+         ]
+ 'time': 0.174407958984375}
+\end{lstlisting}
+For each detected class we return the bounding boxes, the \emph{boxes} key of the json, the class name, its index and the score, the confidence of the model.
+Each box is composed by the top, left, bottom and right coordinate of the bounding box with respect to the left of the image and the top.
+In the above example, the bicyle's bounding starts $96$ pixels from the left and $219$ from the top.
 \section{}
@@
 
-\section{Code}
+\section{Implementation}
+We design our ROS node to find object and follow them until it is close enough.
+In addition, we also implemented a PID based algorithm to avoid obstacle and to stop before crash into the target object.
+From an high level view, the robot can be represented as a three-state machine.
+\begin{figure}[H]
+\centering
+\includegraphics[width=\linewidth]{images/state}
+\caption{State Machine}
+\end{figure}
+Thus, at any time the machine can be \textbf{only} in one of the three states: \emph{exploration}, \emph{obstacle} and \emph{target found}.
+
+\paragraph{Exploration} The robot starts to spin on itself with a fixed angular velocity to scan the surrounding until it finds the target or it detect an obstacle.
+\paragraph{Target Found} When we find the object we are looking for, we start moving towards it by keeping the its bounding box in the camera's center.
+We used a Proportional Integral Derivative, PID, controller to select the correct angular velocity.
+Given the camera's image and the bounding box we define the error at time $t$ as:
+\begin{equation}
+e_t =  (l_b + \frac{w_b}{2}) - \frac{w_c}{2}
+\end{equation}
+Where, $w_c$ is the camera's image width, in our case 640, $l_b$ and $w_b$ are the left component and the width of target's bounding box respectively.
+To find $w_b$ we need to just subtract the the left and right component of the box.
+We are not taking the absolute value of the error since the sign is used to decide in which direction to turn.
+Before feeding  the error to the PID controller we normalise it between zero and one by dividing by $w_c$, otherwise we should have defined a very small proportional parameter for the PID.
+
+After we calculate the error for the current box, we feed it to a PID with a proportional parameter of $0.5$, and integral of $0$ and a derivative of $3$.
+However, even if we did not do any hyperparameter search, we notice that even with smaller values of the derivative component of the PID the robot works properly.
+
+The following figure shows the error for each frame given different position of the target class \emph{bottle}.
+\begin{figure}[H]
+\begin{center}
+	\includegraphics[width=\linewidth]{images/frame_error.png}
+\end{center}	
+\begin{center}
+\includegraphics[width=0.25\linewidth]{images/bottle/1}	
+\includegraphics[width=0.25\linewidth]{images/bottle/2}	
+\includegraphics[width=0.25\linewidth]{images/bottle/3}		
+\end{center}
+\caption{Bounding Box Error}
+\end{figure}
+The error is bigger when the bottle is on the left on the right and it is zero when it is in the center of the image.
+We used it as angular velocity in order to keep the robot pointed to the target object.
+We move it forward with a fixed linear velocity of $0.1$.
+
+\paragraph{Obstacle} When the Thymio's proximity sensors of the Thymios, five in the front and two in the back, detect something it stops any activity and goes into the \emph{Obstacle} state.
+We implemented a simple yet effective PID controllers based algorithm to move the Thymio await from any object in from of it.
+We defined two PIDs, one for the linear velocity and one for the angular.
+The errors are $e_l$ for the linear PID and $e_a$ for the angular PID, defined as follow.
+We denote the front sensor set as $S_f$ and the rear sensor set as $S_r$, where each element in the set is a double representing the value from the sensor.
+In out case, $|S_f| = 5$ and $|S_r|=2$.
+\begin{align}
+	e_l &= \limits\sum_{i=0}^{|S_f|} S_f(i) - \limits\sum_{i = 0}^{|R_f|} R_f(i) \\
+	e_a &= (\limits\sum_{i=0}^{\frac{|S_f|}{2}} S_f(i) - \limits\sum_{i = \frac{|S_f|}{2} }^{|S_f|} S_f(i)) - 
+	(\limits\sum_{i=0}^{\frac{|R_f|}{2}} R_f(i) - \limits\sum_{i = \frac{|R_f|}{2} }^{|R_f|} R_f(i))
+	\end{align}
+
+Also, we turn on the five frontal Thymio's LED as user feedback.The number and position of the LEDs are based on the width of target's bounding box.
+For example, a big object on the left side will turn on two LEDs, while a smaller one only  one.
+The follow picture shows an example where the robot is looking for a \emph{cup}:
+\begin{figure}[H]
+\begin{center}
+
+\includegraphics[width=0.25\linewidth]{images/leds/1}	
+\includegraphics[width=0.25\linewidth]{images/leds/2}	
+\includegraphics[width=0.25\linewidth]{images/leds/3}	
+\end{center}
+\begin{center}
+\includegraphics[width=0.25\linewidth]{images/leds/4}	
+\includegraphics[width=0.25\linewidth]{images/leds/5}
+\end{center}
+\caption{On board LEDs}
+\end{figure}
 

### 2018-06-01 paper/paper.tex
updated paper

--- 2018-05-31 paper/paper.tex
@@
 % on the last page of the document
-
+\usepackage{hyperref}
+\usepackage{listings}
 \usepackage{biblatex}
 \bibliography{paper}
-
+\usepackage{float}
+\usepackage{amsmath}
+\usepackage{graphicx}
 % The following packages can be found on http:\\www.ctan.org
@@
 \begin{abstract}
-The ability to classify in booth space and domain objects is encoded in an enormous variety of species on the planet.
+The ability to classify objects in both space and domain is encoded in an enormous variety of species on the planet.
 Recently, deep learning approaches have been developed to make machines able to mimic the same task with interesting results.
-With this paper, we propose a minimal architecture to archive the same goal using a two wheels robots, the Thymio, with a mounted frontal camera in order to act based on the object detected in the surrounding.
+With this paper, we propose a minimal architecture to archive the same goal using a cheap two wheels robots, the Thymio, with a mounted frontal camera in order to make it act based on the objects detected in the surrounding.
 \end{abstract}
@@
 \section{Introduction}
+Finding objects in space by identifying their identity and their coordinates is a basic task that almost every animal is able to accomplish.
+The ability to solve this problem is extremely important in robotics, where a machine needs to act based on its surrounding.
+We implemented an architecture running on ROS, that is able to find selected targets object by using YOLO, a real-time object detection model,  by only using a cheap camera.
 
-Finding objects in space by identifying their identity and their coordinates is a basic task that almost each animal is able to accomplish by feeding the inputs from their eyes to the brain.
-The ability to solve this problem is extremely important in robotics, where a machine needs to act accordingly based on its surrounding.
-With our architecture, only the raw data from the camera are used as input to an Object Detection model and the decision are based directly on the prediction, without the need of any other sensor.
+Specifically, our robot will wait for an user-specified class, e.g.
+\emph{dog}, and, when found, it moves towards the object by keeping it in the middle of its view.
+We also implemented a PID based algorithm to avoid obstacles and properly stop in front of the founded item.
 
-The paper is structured as follows: we will first describe the architecture by showing each individual part of the topology and how they interact; then, we will discuss the challenges during the development process and finally we will show the results.
+The paper is structured as follows: we will first describe the architecture by showing each individual part of the topology and how they interact; then, we will discuss the challenges during the development process and finally, we will show the results.
 
 \section{Architecture overview}
-
-Our architecture is composed by:
+We used the Robotic Operating System,\cite{ROS}, since its \emph{de facto} the state of the art. Our architecture is composed by:
 \begin{enumerate}
-	\item A robot with a mounted camera and an on-board computer with a running ROS node;
-	\item A web server running the Object Detection model;
-	\item A ROS node running on a local machine.
+	\item A robot with a mounted camera with a ROS node running on the on-board computer
+	\item A web server running the Object Detection model
+	\item A ROS node running on a local machine that controll the robot
 \end{enumerate}
@@
 
-\subsection{Configuration}
+\subsection*{The MightyThymio Robot}
 
 In our project, the MightyThymio has the same configuration proposed in \cite{guzzi2018eaai}.
-On the on-board computer of the robot there is a running ROS node that can publish and subscribe in order to communicate with its sensors: it can have information from the proximity sensors to avoid hitting obstacles, it can take images from the mounted camera, it can use the leds to indicate an object or a direction, and more.
-On the local machine there is another running ROS node that specifies the behaviour of the MightyThymio based on the presence of specific objects around him.
-
+Briefly, the onboard computer exposes the Thymios sensors through ROS.
+Thus, another ROS node can publish and subscribe to it in order to communicate with its sensors.
+For example, we can subscribe to the \emph{camera sensors} to get information from the proximity sensors to avoid hitting obstacles.
+Also, we can simply subscribe to the camera's topic to get both compressed and uncompressed images.
+\begin{figure}[H]
+\centering
+\includegraphics[width=\linewidth]{assembled_myt}	
+\caption{The MightyThymio}
+\end{figure}
 %Subscribe thyme event of camera, from whom compressed images, encoded in strings, then we send to the server, the server decode the compressed images and send prediction.
@@
 
-\subsection{ROS: Robot Operating System}
-ROS is a robotics middleware that provides libraries and tools to help software developers create robot applications by supplying hardware abstraction, device drivers, message-passing, and more.
-One main concepts in ROS is the node, which is included in the level of Computation Graph, the peer-to-peer network of ROS processes that are processing data together.
-Nodes are processes that perform computation; a robot control system usually comprises many nodes, that act as modules.
+\subsection*{Local ROS node}
+We created a new ROS node to communicate with the running node on the MightyThymio to control it accordingly with a specified behavior based on the object detected by the model.
+The user specifies a set of target classes, for example \emph{dog} and \emph{cat}.
+Then our node, after having subscribed to the camera topic of the MightyThymio, sends the fetched image to the model hosted on a Web  Server through an HTTP request and gets a response detected classes and their bounding boxes.
+In the case there is no target object, the robot enters in \texttt{exploration} mode and starts spinning around.
+When one or more of the target classes are found simultaneously, the robot will go towards the target with the biggest bounding box area while keeping it in the center of the camera in order to follow it.
+In addition, we have an obstacle-avoiding algorithm in order to properly stop the Thymio before it hits the target.
 
-\subsection{YOLO: Real-Time Object Detection}
+\subsection*{Object Detection REST-API Web Server}
+We used pre-trained Keras implementation\footnote{https://github.com/qqwweee/keras-yolo3} of YOLO\cite{DBLP:conf/cvpr/RedmonDGF16} model, the state-of-the-art real-time object detection model, with TensorFlow\cite{tensorflow2015-whitepaper} backend to predict the classes in the image and their bounding boxes.
+A bounding box is a rectangle in which the predicted class is contained.
+For example, in the following picture we can see the bounding boxes for a \emph{dog}, a \emph{bicycle} and a \emph{truck}.
+Each box is labeled with the class name and its score.
+\begin{figure}[H]
+\centering
+\includegraphics[width=\linewidth]{images/yolo-example}
+\label{fig: yolo-example}
+\caption{Yolo Prediction Example}
+\end{figure}
+The model was trained on the COCO(Common Object in Context)\cite{COCO} Dataset, that contains 80 classes.
 
-YOLO \cite{DBLP:conf/cvpr/RedmonDGF16} is a trained model for real-time object detection.
+On top of that, we built a REST-API Web Server using Python3 and Flask\footnote{http://flask.pocoo.org/}, a micro-framework to create Web Servers, to make the model accessible from the Web.
+We decided to decouple the logic behind the robot behavior and the model in order to make our architecture more scalable.
+For instance, if needed, we can deploy our model in the cloud while keeping the running ROS code intact.
+
+We following endpoints are available:
+\begin{lstlisting}
+GET /model
+POST /prediction  --image --size --compress
+\end{lstlisting}
+Each of them returns a JSON serialised response.
+The \texttt{/model} endpoint is used to get informations about the model.
+These informations are the classes that can be predicted and the colour associated to each one of them.
+It follows a response sample:
+\begin{lstlisting}
+{
+    "classes": [ "person", "bicycle", "car", "motorbike", "aeroplane", ... ]
+    "colors": [[255, 38, 0], [0, 63, 255], ... ]   
+ }
+\end{lstlisting}
+The client can get a prediction by sending an image to \texttt{/prediction}.
+It is also possible to specify whatever the image is compressed or no and if the server should resize it before feeding it to the model.
+In our case, we send a compressed image directly taken from the MightyThymio after subscribing to the \texttt{/camera/compressed} topic and we define the resize size to (190,190).
+The small size is due to low computational power since we had no access to a GPU.
+By sanding the same image showed in Figure \ref{fig: yolo-example} we get the following response.
+\begin{lstlisting}
+{'res': [{'boxes': [96.21580505371094,
+                    219.6134033203125,
+                    437.66387939453125,
+                    594.16748046875],
+          'class': 'bicycle',
+          'class_idx': 1,
+          'score': 0.48406994342803955}, ...
+         ]
+ 'time': 0.174407958984375}
+\end{lstlisting}
+For each detected class we return the bounding boxes, the \emph{boxes} key of the JSON, the class name, its index, and the score, the confidence of the model.
+Each box is composed of the top, left, bottom and the right offsets of the bounding box with respect to the left of the image and the top.
+In the above example, the bicycle's bounding starts $96$ pixels from the left and $219$ from the top.
+\section{}
+%
+%\subsection{YOLO: Real-Time Object Detection}
+%
+%YOLO \cite{DBLP:conf/cvpr/RedmonDGF16} is a trained model for real-time object detection.
 While prior work on object detection repurposes classifiers to perform detection, YOLO handle the object detection as a regression problem to spatially separated bounding boxes and associated class probabilities.
@@
 Using YOLO, You Only Look Once at an image to predict what objects are present and where they are.
-
-YOLO neural network uses features from the entire image to predict each bounding box simultaneously across all classes.
+%
+%YOLO neural network uses features from the entire image to predict each bounding box simultaneously across all classes.
 The convolutional neural network contains 24 convolutional layers, that extract features from the image, followed by 2 fully connected layers, whose aim is to predict the output probabilities and coordinates.
-The system divides the input image into an $S \times S$ grid; if the center of an object falls into a grid cell, that grid cell is responsible for detecting that object.
+The system divides the input image into an $S \times S$ grid; if the centre of an object falls into a grid cell, that grid cell is responsible for detecting that object.
 Each grid cell predicts $B$ bounding boxes and confidence scores for those boxes.
 These confidence scores reflect how confident the model is that the box contains an object and also how accurate it thinks the box is that it predicts.
-There is also a fast version of YOLO, designed with a neural network with fewer convolutional leayers and fewer filters in those layers.
-
-YOLO is extremely fast, it reason globally about the image when making predictions, it learns generalizable representations of objects and it is open source.
+There is also a fast version of YOLO, designed with a neural network with fewer convolutional layers and fewer filters in those layers.
+%
+%YOLO is extremely fast, it reason globally about the image when making predictions, it learns generalizable representations of objects and it is open source.
 YOLO still lags behind other detection systems in accuracy; while it can quickly identify object in images, it struggles to precisely localize some objects, especially small ones.
 However, it is still the state-of-the-art model for object detection in real-time.
+%
+%For our project, we used the third version of YOLO, or YOLOv3 \cite{Yolo3}, which has been improved by making it a little bigger than before, but more accurate.
 
-For our project, we used the third version of YOLO, or YOLOv3 \cite{Yolo3}, which has been improved by making it a little bigger than before, but more accurate.
+\section{Implementation}
+We design our ROS node to find a specified object and follow it until it is close enough.
+In addition, we also implemented a PID based algorithm to avoid obstacles and to stop before crash into the target object.
+From a high-level view, the robot can be represented as a state machine with three states.
+\begin{figure}[H]
+\centering
+\includegraphics[width=\linewidth]{images/state}
+\caption{State Machine}
+\end{figure}
+Thus, at any time the machine can be \textbf{only} in one of the three states: \emph{exploration}, \emph{obstacle} and \emph{target found}.
 
-\section{Code}
+\paragraph{Exploration} The robot starts to spin on itself with a fixed angular velocity to scan the surrounding until it finds the target or it detect an obstacle.
+\paragraph{Target Found} When a target object is found, the robot starts moving towards it by keeping its bounding box center in the camera's center.
+We used a Proportional Integral Derivative, PID, controller to select the correct angular velocity.
+Given the camera's image and the bounding box, we define the error at time $t$ as:
+\begin{equation}
+e_t =  (l_b + \frac{w_b}{2}) - \frac{w_c}{2}
+\end{equation}
+Where, $w_c$ is the camera's image width, in our case 640, $l_b$ and $w_b$ are the left component and the width of target's bounding box respectively.
+To find $w_b$ we need to just subtract the left and right component of the box.
+We are not taking the absolute value of the error since the sign is used to decide in which direction to turn.
+Before feeding the error to the PID controller we normalize it between zero and one by dividing by $w_c$, otherwise, we should have defined a very small proportional parameter for the PID.
 
-\section{Server}
+After computing the error for the current box, we pass it as parameter to a PID with a proportional parameter set to $0.5$, and integral to $0$ and a derivative to $3$.
+However, even if we did not do any hyperparameter search, we notice that even with smaller values of the derivative component of the PID the robot works properly.
 
-\section{Results}
+The following figure shows the error for each frame given different position of the target class \emph{bottle}.
+\begin{figure}[H]
+\begin{center}
+	\includegraphics[width=\linewidth]{images/frame_error.png}
+\end{center}	
+\begin{center}
+\includegraphics[width=0.31\linewidth]{images/bottle/1}	
+\includegraphics[width=0.31\linewidth]{images/bottle/2}	
+\includegraphics[width=0.31\linewidth]{images/bottle/3}		
+\end{center}
+\caption{Bounding Box Error}
+\end{figure}
+The absolute value of the error is bigger when the bottle is on the left on the right and it is zero when it is in the center of the image.
+We used it as angular velocity in order to keep the robot pointed to the target object.
+We move it forward with a fixed linear velocity of $0.1$.
+
+With these settings we were able to smoothly guide the robot to the target, in the following picture we shown some example frame when the Thymio first see a \emph{cup} on the left and then it moves towards it by keeping it in the middle.
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=0.48\linewidth]{images/cup/1}	
+\includegraphics[width=0.48\linewidth]{images/cup/2}	
+\end{center}
+\begin{center}
+\includegraphics[width=0.48\linewidth]{images/cup/3}	
+\includegraphics[width=0.48\linewidth]{images/cup/4}	
+\end{center}	
+\begin{center}
+\includegraphics[width=0.48\linewidth]{images/cup/5}	
+\includegraphics[width=0.48\linewidth]{images/cup/6}	
+\end{center}	
+\caption{Thymio finds and go to a \emph{cup}}
+\end{figure}
+
+\paragraph{Obstacle} When proximity sensors, five in the front and two in the back, detect something,  the robot stops any activity and goes into the \emph{Obstacle} state.
+We implemented a simple yet effective PID controllers based algorithm to move the Thymio await from any object in front or behind it.
+
+To accomplish this task, we defined two PIDs, one for the linear velocity and one for the angular.
+The errors are $e_l$ for the linear PID and $e_a$ for the angular PID, defined as follow.
+We denote the front sensor set as $S_f$ and the rear sensor set as $S_r$, where each element in the set is a double representing the value from the sensor.
+In our case, $|S_f| = 5$ and $|S_r|=2$.
+\begin{align*}
+	e_l &= \sum\limits_{i=0}^{|S_f|} S_f(i) - \sum\limits_{i = 0}^{|R_f|} R_f(i) \\
+	e_a &= (\sum\limits_{i=0}^{\frac{|S_f|}{2}} S_f(i) - \sum\limits_{i = \frac{|S_f|}{2} }^{|S_f|} S_f(i)) - 
+	(\sum\limits_{i=0}^{\frac{|R_f|}{2}} R_f(i) - \sum\limits_{i = \frac{|R_f|}{2} }^{|R_f|} R_f(i))
+\end{align*}
+The linear error, $e_l$, is just the sum of all the frontal sensors values minus the rear sensors values.
+The angular error is defined as the difference between each pair of sensors on the left and the right.
+In booth equation, we subtract the frontal values from the rear in order to invert the sign of the PID output so when there is an obstacle in front of the robot, the velocity is negative and vice-versa.
+
+As user feedback, we turn on the five frontal Thymio's LEDs.
+The number and position of the LEDs are based on the width of target's bounding box.
+For example, a big object on the left side will turn on two LEDs, while a smaller only one.
+The following figure shows an example where the robot is looking for a \emph{cup}:
+\begin{figure}[H]
+\begin{center}
+
+\includegraphics[width=0.25\linewidth]{images/leds/1}	
+\includegraphics[width=0.25\linewidth]{images/leds/2}	
+\includegraphics[width=0.25\linewidth]{images/leds/3}	
+\end{center}
+\begin{center}
+\includegraphics[width=0.25\linewidth]{images/leds/4}	
+\includegraphics[width=0.25\linewidth]{images/leds/5}
+\end{center}
+\caption{On board LEDs}
+\end{figure}
 \section{Conclusion}
+In this paper, we presented a light and scalable architecture that uses a real-time Object Detection model to correctly find objects in the surrounding environment and to perform actions based on them.
+Moreover, because the only  hardware constraint is the camera, our work can be used into similar robots running ROS  to extend their functionalities.
+Furthermore, since we used YOLO to perform the classification task, the model can be easily re-trained with other classes to increase the context domain.
+This symbiosis between Machine Learning and Robotic highlights the power of both areas by creating new interesting use cases and scenarios in which both disciplines can shine.
 

### 2018-06-01 core/keras-yolo3/it_client.py

@@ -26,7 +26,7 @@ while True:
         src = cv2.imread(img_path)
         image = cv2.cvtColor(src, cv2.COLOR_BGR2RGB)
 
-        res = requests.post('{}/prediction'.format(HOST_URL), json = { 'image' : image.tolist(), 'size' : (192,192) })
+        res = requests.post('{}/prediction'.format(HOST_URL), json = { 'image' : image.tolist(), 'size' : (416,416) })
 
         out_scores, out_boxes, out_classes, out_classes_idx = unbox(res.json())
 

### 2018-06-01 paper/paper.tex
minor changes

@@
 \usepackage{float}
-\usepackage{amsmath}
+\usepackage{amsmath, amsthm, amssymb}
 \usepackage{graphicx}
@@
 We denote the front sensor set as $S_f$ and the rear sensor set as $S_r$, where each element in the set is a double representing the value from the sensor.
-In our case, $|S_f| = 5$ and $|S_r|=2$.
-\begin{align*}
+In our case the cardinalility of each set are $|S_f| = 5$ and $|S_r|=2$.
+\begin{align}
 	e_l &= \sum\limits_{i=0}^{|S_f|} S_f(i) - \sum\limits_{i = 0}^{|R_f|} R_f(i) \\
-	e_a &= (\sum\limits_{i=0}^{\frac{|S_f|}{2}} S_f(i) - \sum\limits_{i = \frac{|S_f|}{2} }^{|S_f|} S_f(i)) - 
-	(\sum\limits_{i=0}^{\frac{|R_f|}{2}} R_f(i) - \sum\limits_{i = \frac{|R_f|}{2} }^{|R_f|} R_f(i))
-\end{align*}
+	e_a &= (\sum\limits_{i=0}^{\frac{|S_f|}{2}} S_f(i) - \sum\limits_{i = \frac{|S_f|}{2} }^{|S_f|} S_f(i))  \\
+	&- (\sum\limits_{i=0}^{\frac{|R_f|}{2}} R_f(i) - \sum\limits_{i = \frac{|R_f|}{2} }^{|R_f|} R_f(i))  \notag
+\end{align}
 The linear error, $e_l$, is just the sum of all the frontal sensors values minus the rear sensors values.

### 2018-06-01 paper/paper.tex
Corrected tex paper

@@
 \usepackage{float}
+\let\proof\relax
+\let\endproof\relax
 \usepackage{amsmath, amsthm, amssymb}
@@
 Recently, deep learning approaches have been developed to make machines able to mimic the same task with interesting results.
-With this paper, we propose a minimal architecture to archive the same goal using a cheap two wheels robots, the Thymio, with a mounted frontal camera in order to make it act based on the objects detected in the surrounding.
+With this paper, we propose a minimal architecture to archive the same goal using a cheap two-wheels robot, the Thymio, with a mounted frontal camera in order to make it act based on the objects detected in the surrounding.
 \end{abstract}
@@
 The ability to solve this problem is extremely important in robotics, where a machine needs to act based on its surrounding.
-We implemented an architecture running on ROS, that is able to find selected targets object by using YOLO, a real-time object detection model,  by only using a cheap camera.
+We implemented an architecture, running on ROS, that is able to find selected target objects through YOLO, a real-time object detection model,  by only using a cheap camera.
 
-Specifically, our robot will wait for an user-specified class, e.g.
+Specifically, our robot will wait for a user-specified class, e.g.
 \emph{dog}, and, when found, it moves towards the object by keeping it in the middle of its view.
-We also implemented a PID based algorithm to avoid obstacles and properly stop in front of the founded item.
+We also implemented a PID-based algorithm to avoid obstacles and properly stop in front of the founded item.
 
-The paper is structured as follows: we will first describe the architecture by showing each individual part of the topology and how they interact; then, we will discuss the challenges during the development process and finally, we will show the results.
+The paper is structured as follows: we will first describe the architecture by showing each individual part of the topology and how they interact; then, we will discuss the challenges during the development process and, finally, we will show the results.
 
 \section{Architecture overview}
-We used the Robotic Operating System,\cite{ROS}, since its \emph{de facto} the state of the art. Our architecture is composed by:
+We used the Robotic Operating System,\cite{ROS}, since it is \emph{de facto} the state of the art. Our architecture is composed by:
 \begin{enumerate}
-	\item A robot with a mounted camera with a ROS node running on the on-board computer
-	\item A web server running the Object Detection model
-	\item A ROS node running on a local machine that controll the robot
+	\item A robot with a mounted camera and with a ROS node running on the on-board computer;
+	\item A web server running the Object Detection model;
+	\item A ROS node running on a local machine that controls the robot.
 \end{enumerate}
@@
 \end{figure}
-%Subscribe thyme event of camera, from whom compressed images, encoded in strings, then we send to the server, the server decode the compressed images and send prediction.
-After prediction, if class is target, for example person, the server send the person and bounding box.
-If the timeo see the person, it moves verso the person keeping her in the centre.
-So if the person moves, the timeo moves to keep the bounding box in the centre of the camera.
-So using only the image we can tell timeo to follow a target, without knowing the position of target or of thimeo.
-%The rod node is a module that can be put where you want.
 
 \subsection*{Local ROS node}
-We created a new ROS node to communicate with the running node on the MightyThymio to control it accordingly with a specified behavior based on the object detected by the model.
+We created a new ROS node to communicate with the running node on the MightyThymio, in order to control it accordingly with a specified behaviour based on the object detected by the model.
 The user specifies a set of target classes, for example \emph{dog} and \emph{cat}.
-Then our node, after having subscribed to the camera topic of the MightyThymio, sends the fetched image to the model hosted on a Web  Server through an HTTP request and gets a response detected classes and their bounding boxes.
-In the case there is no target object, the robot enters in \texttt{exploration} mode and starts spinning around.
+Then our node, after having subscribed to the camera topic of the MightyThymio, sends the fetched image to the model hosted on a Web  Server through an HTTP request and gets as response the detected classes and their bounding boxes.
+In case there is no target object, the robot enters in \texttt{exploration} mode and starts spinning around.
 When one or more of the target classes are found simultaneously, the robot will go towards the target with the biggest bounding box area while keeping it in the center of the camera in order to follow it.
@@
 For example, in the following picture we can see the bounding boxes for a \emph{dog}, a \emph{bicycle} and a \emph{truck}.
-Each box is labeled with the class name and its score.
+Each box is labelled with the class name and its score.
 \begin{figure}[H]
@@
 
-On top of that, we built a REST-API Web Server using Python3 and Flask\footnote{http://flask.pocoo.org/}, a micro-framework to create Web Servers, to make the model accessible from the Web.
+On top of that, we built a REST-API Web Server using Python3 and Flask\footnote{http://flask.pocoo.org/}, a micro-framework to create Web Servers, in order to make the model accessible from the Web.
 We decided to decouple the logic behind the robot behavior and the model in order to make our architecture more scalable.
@@
 
-We following endpoints are available:
+The following endpoints are available:
 \begin{lstlisting}
@@
 Each of them returns a JSON serialised response.
-The \texttt{/model} endpoint is used to get informations about the model.
-These informations are the classes that can be predicted and the colour associated to each one of them.
+The \texttt{/model} endpoint is used to get information about the model.
+These information are the classes that can be predicted and the colour associated to each one of them.
 It follows a response sample:
@@
 The client can get a prediction by sending an image to \texttt{/prediction}.
-It is also possible to specify whatever the image is compressed or no and if the server should resize it before feeding it to the model.
-In our case, we send a compressed image directly taken from the MightyThymio after subscribing to the \texttt{/camera/compressed} topic and we define the resize size to (190,190).
-The small size is due to low computational power since we had no access to a GPU.
+It is also possible to specify if the image is compressed or not and if the server should resize it before feeding it to the model.
+In our case, we send a compressed image directly taken from the MightyThymio after subscribing to the \texttt{/camera/compressed} topic and we define the resized size to (190,190).
+The small size is due to the low computational power since we had no access to a GPU.
 By sanding the same image showed in Figure \ref{fig: yolo-example} we get the following response.
@@
 \end{lstlisting}
-For each detected class we return the bounding boxes, the \emph{boxes} key of the JSON, the class name, its index, and the score, the confidence of the model.
-Each box is composed of the top, left, bottom and the right offsets of the bounding box with respect to the left of the image and the top.
-In the above example, the bicycle's bounding starts $96$ pixels from the left and $219$ from the top.
-\section{}
+For each detected class we return the bounding boxes, the \texttt{boxes} key of the JSON, the class name, its index, and the score, that is the confidence of the model.
+Each box is composed by the top, left, bottom and right offsets of the bounding box with respect to the left and the top of the image.
+In the above example, the bicycle's bounding starts at $96$ pixels from the left and at $219$ pixels from the top.
+
 %
@@
 \section{Implementation}
-We design our ROS node to find a specified object and follow it until it is close enough.
-In addition, we also implemented a PID based algorithm to avoid obstacles and to stop before crash into the target object.
+We designed our ROS node to find a specified object and follow it until it is close enough.
+In addition, we also implemented a PID-based algorithm to avoid obstacles and to stop before crashing into the target object.
 From a high-level view, the robot can be represented as a state machine with three states.
@@
 \end{figure}
-Thus, at any time the machine can be \textbf{only} in one of the three states: \emph{exploration}, \emph{obstacle} and \emph{target found}.
+Thus, at any time, the machine can be \textbf{only} in one of the three states: \emph{exploration}, \emph{obstacle} and \emph{target found}.
 
-\paragraph{Exploration} The robot starts to spin on itself with a fixed angular velocity to scan the surrounding until it finds the target or it detect an obstacle.
-\paragraph{Target Found} When a target object is found, the robot starts moving towards it by keeping its bounding box center in the camera's center.
-We used a Proportional Integral Derivative, PID, controller to select the correct angular velocity.
+\paragraph{Exploration} The robot starts to spin on itself with a fixed angular velocity in order to scan the surrounding until it finds the target or it detects an obstacle.
+\paragraph{Target Found} When a target object is found, the robot starts moving towards it by keeping its bounding box centred in the camera's centre.
+We used a Proportional Integral Derivative (PID) controller to select the correct angular velocity.
 Given the camera's image and the bounding box, we define the error at time $t$ as:
@@
 After computing the error for the current box, we pass it as parameter to a PID with a proportional parameter set to $0.5$, and integral to $0$ and a derivative to $3$.
-However, even if we did not do any hyperparameter search, we notice that even with smaller values of the derivative component of the PID the robot works properly.
+However, even if we did not do any hyperparameter search, we noticed that even with smaller values of the derivative component of the PID the robot works properly.
 
@@
 \end{figure}
-The absolute value of the error is bigger when the bottle is on the left on the right and it is zero when it is in the center of the image.
-We used it as angular velocity in order to keep the robot pointed to the target object.
-We move it forward with a fixed linear velocity of $0.1$.
+The absolute value of the error is bigger when the bottle is on the left or on the right and it is zero when it is in the center of the image.
+We used it as angular velocity in order to keep the robot pointing to the target object.
+We make it move forward with a fixed linear velocity of $0.1$.
 
-With these settings we were able to smoothly guide the robot to the target, in the following picture we shown some example frame when the Thymio first see a \emph{cup} on the left and then it moves towards it by keeping it in the middle.
+With these settings we were able to smoothly guide the robot to the target; in the following picture we show some example frame of the moment when the Thymio first sees a \emph{cup} on the left and then moves towards it by keeping it in the middle of its view.
 \begin{figure}[H]
@@
 
-\paragraph{Obstacle} When proximity sensors, five in the front and two in the back, detect something,  the robot stops any activity and goes into the \emph{Obstacle} state.
-We implemented a simple yet effective PID controllers based algorithm to move the Thymio await from any object in front or behind it.
+\paragraph{Obstacle} When the proximity sensors, five in the front and two in the back, detect something,  the robot stops any activity and goes into the \emph{Obstacle} state.
+We implemented a simple but yet effective PID controller-based algorithm to move the Thymio away from any object in front or behind it.
 
-To accomplish this task, we defined two PIDs, one for the linear velocity and one for the angular.
-The errors are $e_l$ for the linear PID and $e_a$ for the angular PID, defined as follow.
+To accomplish this task, we defined two PIDs, one for the linear velocity and one for the angular velocity.
+The errors are $e_l$ for the linear PID and $e_a$ for the angular PID, defined as follows.
 We denote the front sensor set as $S_f$ and the rear sensor set as $S_r$, where each element in the set is a double representing the value from the sensor.
-In our case the cardinalility of each set are $|S_f| = 5$ and $|S_r|=2$.
+In our case the cardinality of the sets are $|S_f| = 5$ and $|S_r|=2$.
 \begin{align}
@@
 The linear error, $e_l$, is just the sum of all the frontal sensors values minus the rear sensors values.
-The angular error is defined as the difference between each pair of sensors on the left and the right.
-In booth equation, we subtract the frontal values from the rear in order to invert the sign of the PID output so when there is an obstacle in front of the robot, the velocity is negative and vice-versa.
+The angular error is defined as the difference between each pair of sensors on the left and on the right.
+In both the equations, we subtract the frontal values from the rear ones in order to invert the sign of the PID output so that when there is an obstacle in front of the robot, the velocity is negative and vice-versa.
 
-As user feedback, we turn on the five frontal Thymio's LEDs.
-The number and position of the LEDs are based on the width of target's bounding box.
-For example, a big object on the left side will turn on two LEDs, while a smaller only one.
+As a user feedback, we turn on the five frontal Thymio's LEDs.
+The number and position of the LEDs are based on the width and the direction of target's bounding box.
+For example, a big object on the left side will turn on two LEDs, while a smaller object only one.
 The following figure shows an example where the robot is looking for a \emph{cup}:
@@
 Furthermore, since we used YOLO to perform the classification task, the model can be easily re-trained with other classes to increase the context domain.
-This symbiosis between Machine Learning and Robotic highlights the power of both areas by creating new interesting use cases and scenarios in which both disciplines can shine.
+This symbiosis between Machine Learning and Robotics highlights the power of both areas by creating new interesting use cases and scenarios in which both disciplines can shine.
 

### 2018-06-01 paper/paper.tex
addeddguide

@@
 \title{\LARGE \bf
-Object Detection-Based Behaviour using YOLO on Thymio
+Object Detection-Based Behaviour using Deep-Learning on Thymio
 }
 
-%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
-%         \thanks{*Use the $\backslash$thanks command to put information here}\\
-%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
-%         University of Twente\\
-%         7500 AE Enschede, The Netherlands\\
-%         {\tt\small h.kwakernaak@autsubmit.com}}
-%         \hspace*{ 0.5 in}
-%         \parbox{3 in}{ \centering Pradeep Misra**
-%         \thanks{**The footnote marks may be inserted manually}\\
-%        Department of Electrical Engineering \\
-%         Wright State University\\
-%         Dayton, OH 45435, USA\\
-%         {\tt\small pmisra@cs.wright.edu}}
-%}
-
-\author{Francesco Saverio Zuppichini$^{1}$ and Alessia Ruggeri$^{2}$}% <-this % stops a space
+\author{Francesco Saverio Zuppichini$^{1}$ and Alessia Ruggeri$^{2}$% <-this % stops a space
+\thanks{$^{1}$Francesco Saverio Zuppichini, \href{mailto:zuppif@usi.ch}{zuppif@usi.ch} , AI master student at Università della Svizzera Italiana }%
+\thanks{$^{2}$Alessia Ruggeri, \href{mailto:ruggea@usi.ch}{ruggea@usi.ch} , AI master student at Università della Svizzera Italiana }%
+}
 
@@
 Recently, deep learning approaches have been developed to make machines able to mimic the same task with interesting results.
-With this paper, we propose a minimal architecture to archive the same goal using a cheap two-wheels robot, the Thymio, with a mounted frontal camera in order to make it act based on the objects detected in the surrounding.
+With this paper, we propose a minimal architecture to archive the same goal using a cheap two-wheels robot, the Thymio, with a mounted frontal camera in order to make it moves based on the objects detected in the surrounding.
 \end{abstract}
@@
 The \texttt{/model} endpoint is used to get information about the model.
-These information are the classes that can be predicted and the colour associated to each one of them.
+This information are the classes that can be predicted and the colour associated to each one of them.
 It follows a response sample:
@@
 {
-    "classes": [ "person", "bicycle", "car", "motorbike", "aeroplane", ... ]
+    "classes": [ 
+    "person", 
+    "bicycle", 
+    "car", 
+    "motorbike", 
+    "aeroplane", ... ]
     "colors": [[255, 38, 0], [0, 63, 255], ... ]   
@@
 \end{figure}
+A video showing the point of view of the Thymio while moving towards a \emph{cup} can be found at
+
 \section{Conclusion}

### 2018-06-01 paper/paper.tex
latest changes to the paper

@@
 Specifically, our robot will wait for a user-specified class, e.g.
-\emph{dog}, and, when found, it moves towards the object by keeping it in the middle of its view.
+\emph{dog}, and, when it finds it using the object detecttion model on the camera image, it moves towards the object by keeping it in the middle of its view.
 We also implemented a PID-based algorithm to avoid obstacles and properly stop in front of the founded item.
@@
 \end{figure}
-A video showing the point of view of the Thymio while moving towards a \emph{cup} can be found at
-
+A video showing the point of view of the Thymio while moving towards a \emph{cup} can be found \href{https://drive.google.com/open?id=1tZJpsfvfZGCGxunPWGHa3pLJnMj5mfOd}{here}\footnote{\texttt{https://drive.google.com/open?id=1tZJpsfvfZGCGxunPWGHa3pLJnMj5mfOd}}, and the third person view \href{https://drive.google.com/open?id=1Y5PMDQD8Aw0vxOK5yE5YwfiWLsMvXp-t}{here}\footnote{\texttt{https://drive.google.com/open?id=1Y5PMDQD8Aw0vxOK5yE5YwfiWLsMvXp-t}}.
 \section{Conclusion}
@@
 Furthermore, since we used YOLO to perform the classification task, the model can be easily re-trained with other classes to increase the context domain.
-This symbiosis between Machine Learning and Robotics highlights the power of both areas by creating new interesting use cases and scenarios in which both disciplines can shine.
+This symbiosis between Deep Learning and Robotics highlights the power of both areas by creating new interesting use cases and scenarios in which both disciplines can shine.
 

### 2018-06-01 paper/paper.tex
paper finished
minor changes to paper
paper done

@@
 Recently, deep learning approaches have been developed to make machines able to mimic the same task with interesting results.
-With this paper, we propose a minimal architecture to archive the same goal using a cheap two-wheels robot, the Thymio, with a mounted frontal camera in order to make it moves based on the objects detected in the surrounding.
+With this paper, we propose a minimal architecture to achieve the same goal using a cheap two-wheels robot, the Thymio, with a mounted frontal camera in order to make it moves based on the objects detected in the surrounding.
 \end{abstract}
@@
 \emph{dog}, and, when it finds it using the object detecttion model on the camera image, it moves towards the object by keeping it in the middle of its view.
-We also implemented a PID-based algorithm to avoid obstacles and properly stop in front of the founded item.
+We also implemented a PID-based algorithm to avoid obstacles and properly stop in front of the found item.
 
@@
 \section{Architecture overview}
-We used the Robotic Operating System,\cite{ROS}, since it is \emph{de facto} the state of the art. Our architecture is composed by:
+We used the Robotic Operating System,\cite{ROS}, since it is \emph{de facto} the state of the art for robotics. The architecture is composed by:
 \begin{enumerate}
@@
 \subsection*{Local ROS node}
-We created a new ROS node to communicate with the running node on the MightyThymio, in order to control it accordingly with a specified behaviour based on the object detected by the model.
+We created a new ROS node to communicate with the running node on the MightyThymio, in order to control it accordingly with a specific behaviour based on the object detected by the model.
 The user specifies a set of target classes, for example \emph{dog} and \emph{cat}.
@@
 	e_l &= \sum\limits_{i=0}^{|S_f|} S_f(i) - \sum\limits_{i = 0}^{|R_f|} R_f(i) \\
-	e_a &= (\sum\limits_{i=0}^{\frac{|S_f|}{2}} S_f(i) - \sum\limits_{i = \frac{|S_f|}{2} }^{|S_f|} S_f(i))  \\
-	&- (\sum\limits_{i=0}^{\frac{|R_f|}{2}} R_f(i) - \sum\limits_{i = \frac{|R_f|}{2} }^{|R_f|} R_f(i))  \notag
+	e_a &= \sum\limits_{i=0,k=|S_f|}^{\frac{|S_f|}{2}} S_f(i) - S_f(k) - \sum\limits_{i=0,k=|R_f|}^{\frac{|R_f|}{2}} R_f(i) - R_f(k)
+  \notag
 \end{align}
@@
 A video showing the point of view of the Thymio while moving towards a \emph{cup} can be found \href{https://drive.google.com/open?id=1tZJpsfvfZGCGxunPWGHa3pLJnMj5mfOd}{here}\footnote{\texttt{https://drive.google.com/open?id=1tZJpsfvfZGCGxunPWGHa3pLJnMj5mfOd}}, and the third person view \href{https://drive.google.com/open?id=1Y5PMDQD8Aw0vxOK5yE5YwfiWLsMvXp-t}{here}\footnote{\texttt{https://drive.google.com/open?id=1Y5PMDQD8Aw0vxOK5yE5YwfiWLsMvXp-t}}.
+We open-source all the project, the code can be found in our \href{https://github.com/FrancescoSaverioZuppichini/Robotics-Final-Project}{GitHub repository }\footnote{\texttt{https://github.com/FrancescoSaverioZuppichini/Robotics-Final-Project}}.
+
 \section{Conclusion}

### 2018-06-04 paper/paper.tex
fixed 1 typo.

@@
 Recently, deep learning approaches have been developed to make machines able to mimic the same task with interesting results.
-With this paper, we propose a minimal architecture to achieve the same goal using a cheap two-wheels robot, the Thymio, with a mounted frontal camera in order to make it moves based on the objects detected in the surrounding.
+With this paper, we propose a minimal architecture to achieve the same goal using a cheap two-wheels robot, the Thymio, with a mounted frontal camera in order to move it based on the objects detected in the surrounding.
 \end{abstract}
